\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-10-17 eg6-letters/NIM/EG6_RTPC_NIM.tex
more updates to the comments on the nim paper

The new CLAS RTPC is a 250~mm long cylinder of 158~mm diameter, leaving just enough 
room to fit pre-amplifiers between the RTPC outer shell and the solenoid. The 
electric field is directed perpendicularly to the beam direction, 
such that drifting electrons are pushed away from the beam line. These electrons 
are amplified by three layers of cylindrical gas electron multipliers (GEM) and 
detected by the readout system on the external shell of the detector as 
illustrated in Figure~\ref{fig:RTPC_1_4}. The RTPC is segmented into two halves 
with independent GEM amplification systems that cover about 80\% of the 
azimuthal angle.

>>>>

The new CLAS RTPC is a 250~mm long cylinder of 158~mm diameter, leaving just enough 
room to fit pre-amplifiers between the RTPC outer shell and the solenoid. The 
electric field is directed perpendicularly to the beam direction, 
such that drifting electrons are pushed away from the beam line. These electrons 
are amplified by three layers of semi-cylindrical gas electron multipliers 
(GEM)~\cite{Sauli:2016eeu} and detected by the readout system on the external 
shell of the detector as illustrated in Figure~\ref{fig:RTPC_1_4}. The RTPC is 
segmented into two halves with independent GEM amplification systems that cover 
about 80\% of the azimuthal angle.
